```{r}
#| label: setup
library(tidyverse)
library(tidytuesdayR)
library(here)
library(skimr)
library(glue)
library(scales)
library(ggnewscale)
library(ggtext)
library(ggrepel)
library(sysfonts)
library(showtext)
library(fontawesome)
```

```{r}
#| label: setup-plot-fonts
font_add(
  family = "Font Awesome 7 Brands",
  regular = "~/packages/berkeBrand/Font Awesome 7 Brands-Regular-400.otf"
)
showtext_auto()
showtext_opts(dpi = 300)

font_add_google("Montserrat", "monts")
```

```{r}
#| label: import-data
data_netflix <- tt_load('2025-07-29')

data_netflix_movies <- data_netflix$movies
data_netflix_shows <- data_netflix$shows
```

```{r}
#| label: explore-data
# Movies
glimpse(data_netflix_movies)
skim(data_netflix_shows)

# Shows
glimpse(data_netflix_shows)
skim(data_netflix_shows)
```

```{r}
#| label: explore-unique-values
unique(data_netflix_shows$title)
```

Are there any duplicate titles?

```{r}
#| label: explore-duplicate-titles
# Duplicate titles: yes
data_netflix_shows |>
  filter(available_globally == "No") |>
  count(title, sort = TRUE) |>
  print(n = 100)

# Are duplicate titles due to a re-release? Or, some other reason?
# I think the presence of duplicate titles is due to the reports
# used to create the data, most titles are repeated four times.
data_netflix_shows |>
  filter(available_globally == "Yes") |>
  group_by(title, release_date) |>
  count(sort = TRUE) |>
  print(n = 100)
```

Visualization ideas:

* Since this is a two-year snapshot, I don't think we can use release date for anything useful.
* What shows do the best in terms of reach and engagement?

# Data transformation

```{r}
#| label: trsfm-data
data_netflix_shows_total <- data_netflix_shows |>
  filter(available_globally == "Yes") |>
  group_by(title) |>
  summarise(
    total_hours_viewed = sum(hours_viewed),
    total_views = sum(views)
  ) |>
  mutate(title = str_remove(title, " \\/\\/.*")) |>
  arrange(desc(total_views))

print(data_netflix_shows_total, n = 100)
```

```{r}
#| label: summ-avgs-quartiles
data_netflix_shows_total |>
  summarise(
    mean_hours_viewed = mean(total_hours_viewed),
    mean_views = mean(total_views)
  )

quant_hours <- quantile(
  data_netflix_shows_total$total_hours_viewed,
  c(.1, .5, .75, .95, .9985)
)

quant_views <- quantile(
  data_netflix_shows_total$total_views,
  c(.1, .5, .75, .95, .99, .9985)
)
```

```{r}
#| label: vis-text
plot_title <- glue(
  "<span>Competing with sleep: The</span>",
  "<span style='color: #db0000'>NETFLIX</span>",
  "<span>shows driving reach and enagement</span>",
  .sep = " "
)

plot_subtitle <- "A snapshot from late 2023 to the first half of 2025"

# Setup socials for caption
bsky_icon <- "&#xe671"
bsky_username <- "collinberke.bsky.social"
github_icon <- "&#xf09b"
github_username <- "collinberke"
linkedin_icon <- "&#xf08c"
linkedin_username <- "collinberke"

socials <- glue(
  "<span style='font-family:\"Font Awesome 7 Brands\"; color: #ffffff'>{bsky_icon};</span>",
  "<span style='color: #ffffff'>{bsky_username}</span>",
  "<span style='font-family:\"Font Awesome 7 Brands\"; color: #ffffff'>{github_icon};</span>",
  "<span style='color: #ffffff'>{github_username}</span>",
  "<span style='font-family:\"Font Awesome 7 Brands\"; color: #ffffff'>{linkedin_icon};</span>",
  "<span style='color: #ffffff'>{linkedin_username}</span>",
  .sep = " "
)

plot_caption <- glue(
  "<br>Source: Netflix Engagement Reports | #TidyTuesday: 2025-07-29<br>",
  socials
)
```

```{r}
#| label: vis-views-to-time-watched
ggplot() +
  geom_point(
    data = data_netflix_shows_total,
    aes(total_hours_viewed, total_views, color = total_views),
    size = 3,
    alpha = .5
  ) +
  scale_colour_gradient(low = "#CCCCCC", high = "#db0000") +
  new_scale_color() +
  geom_point(
    data = data_netflix_shows_total,
    aes(total_hours_viewed, total_views, color = total_hours_viewed),
    size = 3,
    alpha = .5
  ) +
  scale_colour_gradient(low = "#CCCCCC", high = "#db0000") +
  geom_text_repel(
    data = data_netflix_shows_total |>
      filter(
        total_hours_viewed >= quant_hours[["99.85%"]] |
          total_views >= quant_views[["99.85%"]],
      ),
    aes(total_hours_viewed, total_views, label = title),
    size = 3.5,
    color = "white",
    force_pull = 0,
    segment.curvature = -1e-20,
    arrow = arrow(length = unit(0.01, "npc")),
    hjust = -.8,
    nudge_y = 7000000
  ) +
  scale_x_continuous(
    limits = c(0, NA),
    labels = label_number(scale_cut = cut_short_scale()),
    expand = expansion(mult = c(0, .2))
  ) +
  scale_y_continuous(
    limits = c(0, NA),
    labels = label_number(scale_cut = cut_short_scale()),
    expand = expansion(mult = c(0, .1))
  ) +
  labs(
    x = "Total Hours Viewed",
    y = "Total Views",
    title = plot_title,
    subtitle = plot_subtitle,
    caption = plot_caption
  ) +
  theme_minimal() +
  theme(
    text = element_text(colour = "#ffffff", face = "bold"),
    panel.grid = element_blank(),
    plot.background = element_rect(fill = "black"),
    legend.position = "none",
    axis.text = element_text(color = "#ffffff"),
    axis.title = element_text(color = "#ffffff", size = 10),
    plot.title = element_textbox_simple(color = "#ffffff", size = 20),
    plot.subtitle = element_text(color = "#ffffff", size = 16),
    plot.caption = element_textbox_simple(halign = 1, colour = "#ffffff")
  )
```

```{r}
#| label: vis-output
ggsave(
  filename = here("2025/2025-07-29/vis_netflix-what-we-watch-shows.png"),
  width = 12,
  height = 10
)
```

# Post

Here's my contribution to this week's #TidyTuesday data: What have we been watching on Netflix?

Competing with sleep: The NETFLIX shows driving reach and engagement

📈Plot using #ggplot2
🏷️Labels with help from {ggrepel}
⚖️Scale text formatting using {scales}
🔤Fonts and icons with help from {sysfonts}, {showtext}, and {fontawesome}
🔗Code and data links 👇

#RStats #DataViz #tidyverse #r4ds 1/4

---

🧑‍💻Code:
📊Data: https://github.com/rfordatascience/tidytuesday/blob/main/data/2025/2025-07-29/readme.md

Shoutout to @jenrichmondphd.bsky.social for curating this week's data. Also, thanks to @nrennie.bsky.social and @albertrapp.bsky.social for their blogs about using icons and fonts in #ggplot2 plots. Links to these to follow.

2/4

---

🔗 Adding social media icons to charts with {ggplot2}: https://nrennie.rbind.io/blog/adding-social-media-icons-ggplot2/
🔗 4 Ways to use colors in ggplot more efficiently: https://albert-rapp.de/posts/ggplot2-tips/07_four_ways_colors_more_efficiently/07_four_ways_colors_more_efficiently.html

3/4

---

And yes, Netflix's competitor is sleep: https://www.theguardian.com/technology/2017/apr/18/netflix-competitor-sleep-uber-facebook

4/4
